---
title: "Project Proposal - Reddit comment helpfulness analysis"
author: "Anirudh Chaudhary, Quan Le, Richard More, Hao Nguyen"
date: "January 22, 2020"
output:
  ioslides_presentation:
    widescreen: true
    logo: Reddit_logo_orange.svg #https://upload.wikimedia.org/wikipedia/commons/e/e5/Reddit_logo_orange.svg
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Problem Description
* We want to do a sentiment analysis on the **World News subreddit** 
* It is very interesting because it gives an additional option of "High Score Comments" to Reddit's sorting functionality. With our prediction model, we can also propose high score comments to place at the top of each thread which will save a significant amount of time for users to find useful comments. This will help Reddit be more attractive then Quora or any other forums.

## Data Collection and Transformation
* We will use **RedditExtractoR**, **tidyverse**, and other relevant libraries; no secondary data source.
* Data can be retrieved by supplying the search arguments like so:
```{r echo=TRUE, eval=FALSE}
reddit_links <- reddit_urls(
  subreddit = "worldnews",
  page_threshold = 10)

reddit_thread <- reddit_content(reddit_links$URL)
```
* Data retrieved as a data frame.
* Initial data explorations shows no violation of any tidy rules.
* Since we are dealing with text data, we will need to clean the text to remove stopwords, stemming, etc.

## Analytics Plan
* Data exploration for comments based on posting times and number of comments in threads
* Convert the comment texts to vectors, so we can perform a text analysis on them.
* N-grams, TF-IDF, Sentiment Analysis
* Use Sentiments Analysis to predict which bucket the comments should belong.

## Evaluation Plan
* Wordcloud to get most frequent phrases
* Graphs, histograms for domains
* Sentiment score
