---
title: "Project Proposal - Reddit comment helpfulness analysis"
author: "Anirudh Chaudhary, Quan Le, Richard More, Hao Nguyen"
date: "January 22, 2020"
output:
  ioslides_presentation:
    widescreen: true
    logo: Reddit_logo_orange.svg #https://upload.wikimedia.org/wikipedia/commons/e/e5/Reddit_logo_orange.svg
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Problem Description
* We want to do a sentiment analysis on the **World News subreddit** comments for the different post relating to recent news from all over the World
* It would be interesting to see how the Reddit community is reacting to recent news in light of some attention-seeking events that have happened recently.

## Data Collection and Transformation
* We will use **RedditExtractoR**, **tidyverse**, and other relevant libraries; no secondary data source.
* Data can be retrieved by supplying the search arguments like so:
```{r echo=TRUE, eval=FALSE}
reddit_links <- reddit_urls(
  subreddit = "worldnews",
  page_threshold = 10)

reddit_thread <- reddit_content(reddit_links$URL)
```
* Data retrieved as a data frame.
* Initial data explorations shows no violation of any tidy rules.
* Since we are dealing with text data, we will need to clean the text to remove stopwords, stemming, etc.

## Analytics Plan
* Data exploration for comments based on posting times and number of comments in threads
* Convert the comment texts to vectors, so we can perform a text analysis on them.
* N-grams, TF-IDF, Sentiment Analysis
* Use Sentiments Analysis
  * Positive / Negative
  * Emotion
  * Numeric

## Evaluation Plan
* Wordcloud to get most frequent phrases, sentiment analysis results
* Graphs, histograms for domains
* Sentiment score/count plot
