---
title: "Project Proposal"
author: 
  <small>
   <ul style="list-style-type:none">
    <li> Richard Moore </li>
    <li> Quan Le </li>
    <li> Anirudh Chaudhary </li>
    <li> Hao Nguyen </li>
    </ul>
  </small>
output:
  revealjs::revealjs_presentation:
    theme: simple
    highlight: haddock
    center: true
    transition: slide
    reveal_options:
      slideNumber: true
--- 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T)

#install.packages("revealjs")
#install.packages("RedditExtractoR")
library(tidyverse)
library(dplyr)
library(RedditExtractoR)

#Theme: “default”, “dark”, “simple”, “sky”, “beige”, “serif”, “solarized”, “blood”, “moon”, “night”, “black”, “league”, “white”
```

## Problem Description
- We will use the data retrieving from <https://cran.r-project.org/web/packages/RedditExtractoR/>
- There is no secondary data.
- We want to develop a machine learning model to predict the upvote of a comment in each thread based on available features
- It is very interesting to find and promote the most useful or concerned comment about a thread. Users won’t have to spend too much time reading junk comments and just spend time reading what is useful. This will help reddit be more attractive then Quora or any other forums website

## Data Collection
- First, we will make sure R is in version 3.6.2 because RedditExtractoR is built to be used in that version
- Then we will use the following code to retrieve a thread in reddit.
```{r warning=FALSE, message=FALSE, results='hide'}
reddit_links <- reddit_urls(
  search_terms   = "cute_cats",
  page_threshold = 1
)
```
- After getting the the links, we can access each link comment by using the following
```{r warning=FALSE, message=FALSE, results='hide'}
reddit_thread <- reddit_content(reddit_links$URL[1])
str(reddit_thread)
```

## Data Content 
```{r warning=FALSE, message=FALSE}
str(reddit_thread)
```

## Data Transformation
<b>How will you clean and transform the data?</b>

- First, we will load tidyverse and convert dataframe to tidyverse dataframe.
- Then, we will make sure the dataframe following three tidy rules. If the dataframe violates any of the tidy rules, we will have to fix its violation.

## Analytics Plan: 
- Perform some exploratory data analysis with GGPLOT2 to find any interesting pattern concerning up_voted
- Convert the comment text to vectors, so we can perform an analysis on it.
- Use stepwise feature extraction to make R decide what features we should use for the Machine Learning Model.
- Use Linear Regression, Ridge and Lasso for this problem to find the relationship between features and up_voted
- Use ggplot2, tidyverse, RedditExtractoR, Linear Regression, Ridge and Lasso

## Evaluation Plan: 
- We will take a look at two things to evaluate the model, adjusted R square and RMSE 
Qualitatively, what kind of results do you expect (e.g. plots, figures, tables, etc.)?
- Quantitatively, we hope to achieve from 85% - 95% adjusted R square and  RMSE ~ 5% of mean
- Additionally, we will perform some Ridge or Lasso Regression and compare the adjusted R square and RMSE. Then, we will choose the best model.

# Thank You


